From Reversible Programs to \\ Univalent Universes and Back

### 2021-09-06 Pi/paper/informalOLD.tex
Rename Pi+ to Pi

\paragraph*{Normalization by evaluation.} Consider the following reversible function:
$\Afun{RESET}(b,b_1,\ldots,b_n) = (b \; \underline{\vee} \; (\bigvee_{i=1}^n b_i),b_1,\ldots,b_n)$ where $\vee$ is
logical-or and $\underline{\vee}$ is exclusive-or. The function sets or resets the first bit depending on whether any of
the other bits is true or not. The natural definition for this function is recursive: modulo some re-shuffling of the
bits, the strategy is to examine the bits $b_i$ one-by-one: if we encounter a true value, we negate the first bit and
terminate; otherwise we continue making recursive calls until we reach the last bit at which point we return the
incoming value with no change:

>>>>

\paragraph*{Normalisation by evaluation.} Consider the following reversible function:
$\Afun{RESET}(b,b_1,\ldots,b_n) = (b \; \underline{\vee} \; (\bigvee_{i=1}^n b_i),b_1,\ldots,b_n)$ where $\vee$ is
logical-or and $\underline{\vee}$ is exclusive-or. The function sets or resets the first bit depending on whether any of
the other bits is true or not. The natural definition for this function is recursive: modulo some re-shuffling of the
bits, the strategy is to examine the bits $b_i$ one-by-one: if we encounter a true value, we negate the first bit and
terminate; otherwise we continue making recursive calls until we reach the last bit at which point we return the
incoming value with no change:

### 2021-09-06 Pi/paper/univalentOLD.tex
Rename Pi+ to Pi

\vc{I'm explaining everything starting from the categorical language. We do care more about the groupoid structure of
  types, and how to encode groupoids using types, since that's what we use in~\cref{sec:finite}.}

@@

\begin{example}[$\BAut$]
  The type of self-equivalences on a type $T$ is defined as $\Aut[T] \defeq T \eqv T$, which is an $\infty$-group. The
  subuniverse of types that are merely equal to $T$ is given by $\BAut[T] \defeq \Sub{T}$. This turns out to be the
  classifying space of $\Aut[T]$, as justified by~\cref{lem:loop-deloop}. We write $T_{o} \defeq (T, \trunc{\refl_{T}})$
  for the image of the inclusion of $T$.
\end{example}

@@

\begin{corollary}
  $\UFin$ is a 1-type, that is, a 1-groupoid, or has h-level 3.
\end{corollary}

>>>>

\vc{I'm explaining everything starting from the categorical language. We do care more about the groupoid structure of
  types, and how to encode groupoids using types, since that's what we use in~\Cref{sec:finite}.}

@@

\begin{example}[$\BAut$]
  The type of self-equivalences on a type $T$ is defined as $\Aut[T] \defeq T \eqv T$, which is an $\infty$-group. The
  subuniverse of types that are merely equal to $T$ is given by $\BAut[T] \defeq \Sub{T}$. This turns out to be the
  classifying space of $\Aut[T]$, as justified by~\Cref{lem:loop-deloop}. We write $T_{o} \defeq (T, \trunc{\refl_{T}})$
  for the image of the inclusion of $T$.
\end{example}

@@

\begin{proposition}
  For any $T : \UU$, $\BAut[T]$ is 0-connected.
\end{proposition}

\begin{corollary}
  $\UFin$ is a pointed, connected, 1-type, that is, a 1-groupoid, or has h-level 3.
\end{corollary}
